### 2025-07-01 index.qmd
20250701 - visualize regression coefficients

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "sn", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply", "SimDesign"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", "mgcv", 
  "rms", "car", "performance", "lavaan", "mice", "miceadds", "interactions", 
  "shiny", "PearsonDS", "robustbase", "data.table", "future", "future.apply", 
  "QuantPsyc", "SimDesign"
)

### 2025-07-01 mixed-models.qmd
20250701 - visualize regression coefficients

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

@@

>>>>

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); cmdstanr::check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("broom.mixed")
library("tidybayes")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

##### Regression Coefficients {#sec-fantasyPointsByAgeExperienceModelsRegressionCoefficients}

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package, as in @fig-individualFantasyPointsRandomLinearFixedQuadraticSlopesInteractionCoefficients.

```{r}
#| label: fig-individualFantasyPointsRandomLinearFixedQuadraticSlopesInteractionCoefficients
#| fig-cap: "Regression Coefficients with 95% Confidence Interval from a Mixed Model With Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes in Interaction With Position. Overlaid with the Model-Implied Trajectory by Position."
#| fig-alt: "Regression Coefficients with 95% Confidence Interval from a Mixed Model With Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes in Interaction With Position. Overlaid with the Model-Implied Trajectory by Position."
#| code-fold: true

pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience_tidy <- broom.mixed::tidy(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  effects = "fixed",
  conf.int = TRUE)

ggplot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Regression Coefficients with 95% CI",
    y = "Coefficient Estimate",
    x = "") +
  theme_minimal()
```

@@

#### Plot of Regression Coefficients {#sec-fantasyPointsByAgeExperienceModelsBayesianRegressionCoefficients}

To visualize the regression coefficients, we can use the `tidy()` function of the `broom.mixed` package, as in @fig-bayesianRegressionCoefficients.

```{r}
#| label: fig-bayesianRegressionCoefficients
#| fig-cap: "Regression Coefficients with 95% Credible Interval from Bayesian Mixed Model."
#| fig-alt: "Regression Coefficients with 95% Credible Interval from Bayesian Mixed Model."

bayesianMixedModelFit_tidy <- broom.mixed::tidy(
  bayesianMixedModelFit,
  effects = "fixed",
  conf.int = TRUE)

ggplot(
  bayesianMixedModelFit_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Posterior Distributions and 95% Credible Intervals",
    x = "Predictor",
    y = "Posterior Estimate") +
  theme_minimal()
```

To visualize the distribution of regression coefficients, we can use the `tidybayes` package, as in @fig-bayesianRegressionCoefficientsDistributions.

```{r}
#| label: fig-bayesianRegressionCoefficientsDistributions
#| fig-cap: "Distributions of Regression Coefficients with 66% (Thin Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."
#| fig-alt: "Distributions of Regression Coefficients with 66% (Thin Line) and 95% (Thin Line) Credible Intervals from Bayesian Mixed Model."

bayesianMixedModelFit %>%
  tidybayes::tidy_draws() %>%
  select(starts_with("b_")) %>%
  pivot_longer(
    everything(),
    names_to = "term",
    values_to = "estimate") %>%
  mutate(term = sub("^b_", "", term)) %>%
  ggplot(
    aes(
      x = estimate,
      y = term)) +
  stat_halfeye() + # by default, .width shows the 66% (thick line) and 95% (thin line) credible intervals
  labs(
    title = "Posterior Distributions of Regression Coefficients with 66% and 95% Credible Intervals",
    x = "Predictor",
    y = "Posterior Estimate") +
  theme_minimal()
```

### 2025-07-01 multiple-regression.qmd
20250701 - visualize regression coefficients

To visualize the regression coefficients, we can use the `tidy()` function of the `broom` package.

```{r}
quadraticTermsRegressionModel_tidy <- tidy(
  quadraticTermsRegressionModel,
  conf.int = TRUE)

quadraticTermsRegressionModelStandardized_tidy <- tidy(
  quadraticTermsRegressionModelStandardized,
  conf.int = TRUE)
```

>>>>

To visualize the regression coefficients, we can use the `tidy()` function of the `broom` package, as in Figures [-@fig-regressionCoefficients] and [-@fig-regressionCoefficientsStandardized].

```{r}
quadraticTermsRegressionModel_tidy <- broom::tidy(
  quadraticTermsRegressionModel,
  conf.int = TRUE)

quadraticTermsRegressionModelStandardized_tidy <- broom::tidy(
  quadraticTermsRegressionModelStandardized,
  conf.int = TRUE)
```
